Ms 1

### 2017-11-10 ms1/ms1_display.Rmd
small display

claims_by_fill %>%
  kable(caption='PDEs by refill')

#  mutate(cum_n=prettyNum(cumsum(n_pde), big.mark=',')) %>%
```

@@

abx_levels = levels(claims_by_abx$abx)

@@

dx_to_pde_trends = read_tsv('tables/dx_to_pde_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(or=   exp(estimate),
         or_lo=exp(ci_lo),
         or_hi=exp(ci_hi)) %>%
  left_join(filter(dx_to_pde_table, year==2011), by=c('dx_cat', 'abx')) %>%
  mutate(rr=   risk_ratio_f(or,    f_with_abx),
         rr_lo=risk_ratio_f(or_lo, f_with_abx),
         rr_hi=risk_ratio_f(or_hi, f_with_abx)) %>%
  mutate(y=rr2pct(rr),
         ymin=rr2pct(rr_lo),
         ymax=rr2pct(rr_hi)) %>%
  mutate(change=sprintf('%.2f (%.2f -- %.2f)', y, ymin, ymax)) %>%
  select(dx_cat, abx, change)
```

@@

combined_table = dx_to_pde_table %>%
  mutate(f_with_abx=format_pct(f_with_abx)) %>%
  spread(year, f_with_abx) %>%
  left_join(dx_to_pde_trends, by=c('dx_cat', 'abx')) %>%
  arrange(abx, dx_cat)
```

>>>>

claims_by_fill %>%
  mutate_at(vars(-f_refill), function(x) prettyNum(x, big.mark=',')) %>%
  kable(caption='PDEs by refill')
```

The top 10 drugs take up `r round(scan('tables/top10_cumf.txt') * 100, 2)`% of all claims.

@@

claims_by_abx %>%
  mutate(cpkp=round(cpkp)) %>%
  spread(year, cpkp) %>%
  kable(caption='Raw drug CPKP')
```

```{r raw_drug_trends_figure}
abx_levels = levels(claims_by_abx$abx)

@@

dx_to_pde_trends = read_tsv('tables/dx_to_pde_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(or=   exp(estimate),
         or_lo=exp(ci_lo),
         or_hi=exp(ci_hi)) %>%
  left_join(filter(dx_to_pde_table, year==2011), by=c('dx_cat', 'abx')) %>%
  mutate(rr=   risk_ratio_f(or,    f_with_abx),
         rr_lo=risk_ratio_f(or_lo, f_with_abx),
         rr_hi=risk_ratio_f(or_hi, f_with_abx)) %>%
  mutate(y=rr2pct(rr),
         ymin=rr2pct(rr_lo),
         ymax=rr2pct(rr_hi)) %>%
  mutate(change=sprintf('%.2f (%.2f -- %.2f)', y, ymin, ymax)) %>%
  select(dx_cat, abx, change, p.value)
```

@@

combined_table = dx_to_pde_table %>%
  mutate(f_with_abx=format_pct(f_with_abx)) %>%
  spread(year, f_with_abx) %>%
  left_join(dx_to_pde_trends, by=c('dx_cat', 'abx')) %>%
  mutate(p.value=format_p(p.value)) %>%
  arrange(abx, dx_cat)
```
